Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-03 paper.Rnw
updated code for creating/loading static figures

<<converting-static-figs-to-eps>>=

# Convert the bullet figure to eps (if needed)
if (!file.exists("./figure-static/figure-08.eps")) {
  bullets <- image_read("./figure-static/figure-08.png")
  image_write(bullets, path = "./figure-static/figure-08.eps", format = "eps")
}

# Convert the signature figure to eps (if needed)
if (!file.exists("./figure-static/figure-09.eps")) {
  signatures <- image_read("./figure-static/figure-09.png")
  image_write(signatures, path = "./figure-static/figure-09.eps", format = "eps")
}

\begin{figure}[!t]
\centering
\includegraphics[width=2.25in]{./figure-static/figure-08.eps}
\caption{(Top left) Traditionally rifled gun barrel. The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired. (Top right) Image of a fired bullet. The vertical stripes along the lower half of the bullet show groove and land engraved areas. The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun. (Bottom) Close up of a land engraved area showing striations (vertical lines).}
\label{fig:figure-08}

@@

\includegraphics[width=2.25in]{./figure-static/figure-09.eps}
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

# Create (or load) the parallel coordinate plot
if (file.exists("./figure-static/figure-10.eps")) {

  # Load and print the plot
  knitr::include_graphics("./figure-static/figure-10.eps")

@@

  # Load the figure and then save as an eps file
  bullet_pcp <- image_read("./figure-static/figure-10.png")
  image_write(bullet_pcp, path = "./figure-static/figure-10.eps", format = "eps")

>>>>

\begin{figure}[!t]
\centering
<<figure-08, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=

# Convert the bullet figure to eps (if needed)
if (!file.exists("./figure-static/figure-08-1.eps")) {
  bullets <- image_read("./figure-static/figure-08-1.png")
  image_write(bullets, path = "./figure-static/figure-08-1.eps", format = "eps")
}

# Load and print the plot
knitr::include_graphics("./figure-static/figure-08-1.eps")

@
\caption{(Top left) Traditionally rifled gun barrel. The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired. (Top right) Image of a fired bullet. The vertical stripes along the lower half of the bullet show groove and land engraved areas. The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun. (Bottom) Close up of a land engraved area showing striations (vertical lines).}
\label{fig:figure-08}

@@

<<figure-09, out.width = '3.125in', fig.width = 6, fig.height = 3, warning = FALSE>>=

# Specify the figure size (for determining font size)
f9_ow = 3.125
f9_fw = 6
f9_fs = fs * (f9_fw / f9_ow)

# Load the signatures data
signatures <- readRDS("../data/signatures.rds")

# Create plot of the signatures
signatures %>%
  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(land~.) +
  ylim(c(-4,6)) +
  theme_bw(base_family = "Times", base_size = f9_fs) +
  theme(strip.background = element_blank()) +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)")

@
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

# Create (or load) the parallel coordinate plot
if (!file.exists("./figure-static/figure-10-1.png")) {

@@

# Create (or load) the parallel coordinate plot
if (file.exists("./figure-static/figure-10-1.eps")) {

  # Load and print the plot
  knitr::include_graphics("./figure-static/figure-10-1.eps")

  # Load the figure and then save as an eps file
  bullet_pcp <- image_read("./figure-static/figure-10-1.png")
  image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")
